\clearpage\secly{Problem of complexity}

\begin{itemize}
  \item 
Complexity is grows and never lows
  \item
Overall complexity of software system is constant value
  \item
Metaprogramming is cool thing, but it gives complexity boost
\end{itemize}
\noindent
So in principle, you can't find any tool which will simplify your life in
programming, if you target a whole system design. The one thing we can do is
move complexity between parts of the system.

From the viewpoint of the application programmer, programming language compiler
and libraries can make programming extra easy\ --- you can just inherit some
application template and do an adaptation in a few lines of source code. But in
fact, we just moved complexity to the compiler and made it more unportable and
complex in design and support. With growing number of hardware and software
platforms, we need to do a giant effort to support one more platform in our
compiler.

If we want to do some experiments at development toolchain level, like runtime
debug and tracking optimization, or add some programming language feature, it is
more suitable to have an \textit{extra simple compiler} (\F\ \ref{whyFORTH}\
language is the best in this case). But \emph{the whole complexity moves to
source code level}: we've got huge source code files written in a cryptic
low-level language. And we must do a lot of things manually. Programs become
huge, buggy and unsupportable.

Metaprogramming is cool technique if your job is making a lot of typical
applications shares common code parts. So if you can distinguish a lot of
template-like code in your sources, you need a language with metaprogramming
capabilities. And it is not about macro\ --- \emph{you must have full scripting
at compile time} and access to your program code in the source code,
intermediate program representation, compiler structures and control on
compiling process itself.

But \emph{metaprogramming is} complex thing by design\ --- it is much simpler to
write program by hands, then \emph{write program that writes program}.

